Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-12-05 paper.tex
Update Fig. 12 HMNS K^r, with new compute-eta data

\begin{figure}
  \includegraphics[width=\columnwidth]{theta_distrib-250km-Kr}
  % Data_a:   $DIR/PositionDistributions/*Lev1-e30a120b20-01*
  % Data_s:   $DIR/PositionDistributions/*Lev1-e30a60b10-01*
  % Data gathered using: $DIR/CollectPositionDistributions.sh
  % Script: $DIR/GnuScripts/plot-theta_distributions-Kr-fixed_r.gnu
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170324-ray_tracing_nsns/Run03
  \caption{Radial number fluxes, $K^r(\theta)$,
    as defined in Eqn.~\ref{eqn:Kr_minkowski},
    in the hypermassive neutron star configuration
    (presented in Sec.~\ref{ssec:test_disk_comparison}).
    Sampled for observers at fixed coordinate distances from the center
    of the star, with $r=250\,{\rm km}$.
  }
  \label{fig:nsns_theta_distrib_Kr}
\end{figure}

>>>>

\begin{figure}
  %\includegraphics[width=\columnwidth]{theta_distrib-250km-Kr}
  \resizebox{\columnwidth}{!}{\input{theta_distrib-250km-Kr.tex}}
  % Data_a:   $DIR/PositionDistributions/*Lev2-e30a150b20-noscat-04*
  % Data_s:   $DIR/PositionDistributions/*Lev2-e30a150b20-scat-04*
  % Data gathered using: $DIR/CollectPositionDistributions.sh
  % Script: $DIR/GnuScripts/plot-theta_distributions-Kr-fixed_r.gnu
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170324-ray_tracing_nsns/Run03
  \caption{Radial number fluxes, $\tilde{K}^r(\theta)$,
    as defined in Eqn.~\ref{eqn:Kr_minkowski},
    in the hypermassive neutron star configuration
    (presented in Sec.~\ref{ssec:test_disk_comparison}).
    Sampled for observers at fixed coordinate distances from the center
    of the star, with $r=250\,{\rm km}$.
  }
  \label{fig:nsns_theta_distrib_Kr}
\end{figure}
